Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-10-07 doc/manuscript/manuscript.Rmd
update cls file to include current aff
this is for lack of a better way to do this atm
Typo
Change NaOCL to NaOCl

  \newaff{second}{Plant Pathology Department, University of Florida, Gainsville, FL 32611}

@@

# Genotype Diversity Table ------------------------------------------------

@@

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or wmn in 11 states of the United States of America, Mexico, France, and Australia (Table \@ref(tab:isolate-table)). 
After collection, sclerotia were stored in Petri plates lined with filter paper, then stored at $20~^{\circ}$F or -$4~^{\circ}$C. 
Sclerotia were surface-sterilized with 50% Clorox bleach (at least 6% NaOCL, The Clorox Company, Oakland, CA) solution for 3 min, and double rinsed with ddH$_2$O for 3 min.
The sterilized sclerotia were then placed on water agar plates (16g of Bacto agar per liter of ddH$_2$O, BD Diagnostic Systems, Sparks, MD), with four to five sclerotia of each isolate separated on each plate and stored on the counter top at room temperature for 5 to 6 days. 
An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH$_2$O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].

>>>>

@@

# Genotype Diversity Table -----------------------------------------------

@@

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or wmn in 11 states of the United States of America, Mexico, France, and Australia (Table \@ref(tab:isolate-table)). 
After collection, sclerotia were stored in Petri plates lined with filter paper, then stored at $20~^{\circ}$F or -$4~^{\circ}$C. 
Sclerotia were surface-sterilized with 50% Clorox bleach (at least 6% NaOCl, The Clorox Company, Oakland, CA) solution for 3 min, and double rinsed with ddH$_2$O for 3 min.
The sterilized sclerotia were then placed on water agar plates (16g of Bacto agar per liter of ddH$_2$O, BD Diagnostic Systems, Sparks, MD), with four to five sclerotia of each isolate separated on each plate and stored on the counter top at room temperature for 5 to 6 days. 
An 8-mm plug from a 5- or 6-day-old culture was transferred from the advancing margin of the mycelia onto a plate of Difco potato dextrose agar (PDA at 39 g/liter of ddH$_2$O) [@otto-hanson2011variation].
In combination with the 156 isolates described previously, we collected 210 isolates for a total of 366 isolates [@otto-hanson2011variation].
